|

### 2021-12-16 04-Chp-Systematic-Review-Results.Rmd
Proofreading edits

In the four analyses with greater than 10 results, the minimum required for subgroup analysis, stratification by overall risk-of-bias level did not demonstrate a difference between the "Serious" and "Moderate" risk of bias groups. The results of the test for subgroup differences is shown in the bottom left of the forest plots for these four meta-analyses (Figures \@ref(fig:obsHyperDementia), \@ref(fig:obsStatinDementiaFig), \@ref(fig:obsHyperAD) and \@ref(fig:obsStatinADFig)).

@@

<!-- TODO Improve caption for the legend below -->

@@

Investigation of potential sources of heterogeneity was complicated by two factors. In the first instance, a minority of meta-analysis (4 out of 18, `r paste0(comma(4/18*100),"%")`) included 10 or more results, the recommended minimum required for meta-regression. Secondly, poor reporting of baseline characteristics of interest precluded the use of several results in a meta-regression analysis.

Only for the sex covariate were sufficient number of results available to enable meta-regression. Across the four meta-analyses examined, the percentage of females in the study cohort was not related to the observed effect estimate (p = `r metaregHypercholDem` for hypercholesterolemia/all-cause dementia, Figure \@ref(fig:obsHyperDementia); p = `r metaregStatinsDem` for statins/all-cause dementia - Figure \@ref(fig:obsStatinDementiaFig); p = `r metaregHypercholAd` for hypercholesterolemia/Alzheimer's disease - Figure \@ref(fig:obsHyperAD); p = `r metaregStatinsAd` for statins/Alzheimer's disease - Figure \@ref(fig:obsStatinADFig)).

Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was limited to these four meta-analyses including 10 or more results. However, there was weak evidence for the presence of small-study effects in each analyses assessed (see Appendix \@ref(appendix-funnel-plots)).

>>>>

In the three analyses with greater than 10 results (Figures \@ref(fig:obsHyperDementia), \@ref(fig:obsStatinDementiaFig) and \@ref(fig:obsStatinADFig)), stratification by overall risk-of-bias level did not demonstrate a difference between the "Serious" and "Moderate" risk of bias groups. The result of the test for subgroup differences is shown in the bottom left of the forest plots for these three meta-analyses.

@@

@@

Investigation of potential sources of heterogeneity was complicated by two factors. In the first instance, a minority of meta-analysis (3 out of 18, `r paste0(comma(3/18*100),"%")`) included 10 or more results, the recommended minimum required for meta-regression. Secondly, poor reporting of baseline characteristics of interest precluded the use of several results in a meta-regression analysis.

Only for the sex covariate were sufficient number of results available to enable meta-regression. Across the three meta-analyses examined, the percentage of females in the study cohort was not related to the observed effect estimate (p = `r metaregHypercholDem` for hypercholesterolemia/all-cause dementia, Figure \@ref(fig:obsHyperDementia); p = `r metaregStatinsDem` for statins/all-cause dementia - Figure \@ref(fig:obsStatinDementiaFig); p = `r metaregStatinsAd` for statins/Alzheimer's disease - Figure \@ref(fig:obsStatinADFig)).

Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was limited to these three meta-analyses including 10 or more results. However, there was weak evidence for the presence of small-study effects in each analyses assessed (see Appendix \@ref(appendix-funnel-plots)).
